%!TEX root=../main.tex
\chapter{Introduction}

\section{Motivation}
\label{sec:mot}
For each new smartphone model, the limits of smartphone processors regarding computational power and energy efficiency are pushed. As a result, processors for mobile devices, or so-called heterogeneous multicores, have gained interest as components in systems outside the mobile market. The \gls{mb} Project \cite{MB} has shown that heterogeneous multicores are potential candidates for building \gls{hpc} systems, as the performance gap between heterogeneous multicores and microprocessors is closing quickly \cite{a:MB:Raj13}. Increasing performance has always been a priority in HPC, and HPC system performance is expected to hit Exascale performance ($10^{18}$ \gls{flops} (exaFLOPS)) within few years \cite{TOP500}. The main goal of the \gls{mb} project is to build a new type of supercomputer architecture, reaching Exascale performance using 15 to 30 times less energy compared to other HPC systems. The project has already constructed multiple prototypes by using heterogeneous processors like the Samsung Exynos \cite{EXY} processor among others. The Barcelona Supercomputing Center coordinates the project, and the project is funded until September 2016. \\

Making energy efficient systems poses enormous challenges for both hardware and software developers. However, ARM among others have made progress in producing energy efficient hardware. ARM has developed energy aware big.LITTLE technology for their heterogeneous cores, which consists of both high performance and energy efficient processors. The technology uses Global Task Scheduling to assign threads to the most appropriate CPU based on dynamic runtime information \cite{a:ARM:bL}. Other well-known hardware techniques are also massively used, such as Dynamic Voltage and Frequency Scaling. Among development of energy efficient software, Task-Based Programming models like OmpSs \cite{a:ompss2013} have gained increasing interest in recent time, and have been used to develop task based programs for heterogeneous architectures \cite{a:Lien2012}. Both research areas are expected to become even more important in the future. \\

There will be an increased need for programmers skilled in developing energy efficient code for heterogeneous multicores. Many \glspl{oj} such as PKU Online Judge \cite{PKU} and Kattis \cite{KATTIS} has existed for years, making it possible for programmers to compete, and self-educate in creating efficient code. However, none of the \glspl{oj} we are aware of are known to evaluate and focus on energy efficiency of submitted programs. Noticing the need for such an \gls{oj}, Lasse Natvig started the \gls{cmb} project to train programmers in developing energy efficient code for heterogeneous multicores by providing a new \gls{oj}. Torbjørn Follan and Simen Støa developed the first prototype version during the Spring of 2015 \cite{mt:T&S}. Previous user testing has, however, shown that usability improvements are needed in some of the system components. \\

The \gls{cmb} project wants to stimulate students and programmers to develop energy efficient high-performance code for heterogeneous multicores. The PKU Online Judge \cite{PKU} had almost a total of 1.3 million submissions last year, and we believe that increasing the number of submissions on the CMB system might help to solve some of the challenges related to programming heterogeneous multicores. An important factor in motivating use of the system, is believed to be achieved by improving system usability. This thesis aims to further improve the system and extend with more functionality with a focus on usability. \\

\section{Problem Statement Interpretation}
\label{sec:ps-inter}
Three different types of objectives are identified in the problem statement. Usability improvements are the main focus of this thesis and there are several tasks listed in the problem statement that can be interpreted as usability tasks. Further, there are tasks not strictly related to usability that can instead be viewed as general improvements to the system. Finally, the thesis aims to propose a series of improvements and implement them if time permits. The subtasks listed below will, as of the above discussion, either be labeled as \textbf{U} for usability, \textbf{I} for improvements, or \textbf{P} for improvement proposals. As the tasks were already prioritized by the supervisor in the problem statement, the tasks listed in secondary objectives are assumed to be less important compared to the main objectives. However, they are of importance to the \gls{cmb} project in general.

\paragraph*{Main objectives} \hfill

\paragraph*{U1} Fix the main bugs and known issues found during user testing of \gls{cmb} in November 2015:
  \begin{itemize}
    \item \textbf{U1.1 Uploads on Mac OS X}: Do not work and give an uninformative error message.
    \item \textbf{U1.2 Submissions locked in a running state}: There should be a timeout on submissions containing infinite loops or code which may leave the submission in a inconsistent state.
    \item \textbf{U1.3 Highscore list bug}: When switching the sort metric, private submissions should still be hidden.
  \end{itemize}

\paragraph*{I1} Change and/or optimize the existing \gls{dbms} if necessary to handle more frequent user submissions. Early in this thesis we discovered that optimizing the database was not as important at this point as first predicted, as the system is still a prototype and we have few active users on the system. As a result, we did not think that optimizing the database was of importance at this point. However, switching to a more sophisticated \gls{dbms} should still be done.

\paragraph*{U2} Improve and extend the CMB system's usability features in accordance with the CMB team's priorities. The features prioritized by the CMB team is a combination of features found during the specialization project, previous user feedback, and necessary usability features discovered throughout the semester:
  \begin{itemize}
    \item \textbf{U2.1 Improved feedback during errors}: Error messages should be structured, clear, and visible.
    \item \textbf{U2.2 Add support for real-time updates during submission execution}: State of submissions should update in real-time without the need of manually refreshing web-content to check for state changes.
    \item \textbf{U2.3 Newly added problems should be more stable}: Problem files added through the admin interface sometimes behaved strange during the semester, such that the success of submissions on the problem seemed random even with a correct implementation.
    \item \textbf{U2.4 Bulletin board extension}: A bulletin board is needed to display administrator messages to the CMB users.
    \item \textbf{U2.5 Views upgrade}: Views should only display necessary information to users. It is also important that users are satisfied with the judge's user interface.
  \end{itemize}

\paragraph*{U3} Conduct a user-experiment to evaluate system usability, and compare results with a previously conducted user test in the specialization project to evaluate the work done in this thesis.

\paragraph*{Secondary objectives} \hfill

\paragraph*{P1} Propose improvements to the existing stability test with a practical solution for simulating users and their submissions, i.e., a synthetic workload.

\paragraph*{P2}  Propose changes to the HowTo information, and how to improve the existing database of problems by cleaning up and improving problem descriptions using experience gained during the system's use in TDT4200 \cite{TDT4200}. Add new problems if time permits.

\paragraph*{P3} Propose how to implement a discussion forum which allows discussion of each problem and the use of CMB in general.

\paragraph*{I2} Implement some of the proposed solutions after approval by, and in collaboration with the CMB team. \\

\section{Project Contributions}
\label{sec:cont}
This project contributes towards improving the usability of the Climbing Mont Blanc system. We define usability as the ease of use, ease of learning, satisfaction of a software system, as well as user error rates. \Cref{ch:design} presents the definition of usability used in this thesis. This thesis also assumes that the usability of a software system is extended if more features are added to the system frontend, since the range of possible actions for users is extended. Usability is a broad term and there is always room for usability improvements in a software system. This thesis is restricted to improve a subset of prioritized usability aspects prior to its the start, as well as urgent usability aspects discovered throughout the work on this thesis. \\

Users of the system is defined as both administrators using the admin interface, and regular users using the frontend browser interface (the website \url{https://climb.idi.ntnu.no}). Furthermore, this thesis also aims to further extend the functionality of the system with focus on contributing towards usability. All contributions and their corresponding sections are summarized in Table \ref{tab:contributions}. \\

It is also worth mentioning that contributions have been made to the \gls{cmb} project, which are not related to the objectives set in \Cref{sec:ps-inter}. A rough estimate of said contributions is calculated to be around 15\%; about 5\% of the time was spent on helping other Master students with development or usage of the system, and 10\% was spent on maintaining the system, as well as attending meetings to plan the future of the \gls{cmb} project. These contributions are not discussed.

%awesome table
\begingroup
\renewcommand{\arraystretch}{1.4}
\begin{table}[t!]
    \centering
    \begin{tabular}{  p{2.0cm} | p{7.0cm} | p{1.9cm} }
    \textbf{Objective} & \textbf{Description Summary}  & \textbf{Section(s)} \\ \hline \hline
    \texttt{U1} & Fix the main bugs and known issues found during previous user testing of \gls{cmb}. & \Cref{sub-sec:impr-frontend-bug} and \ref{sec:impr-backend} \\
    \texttt{I1} & Switch the \gls{dbms} system used by the \gls{cmb} system. & \Cref{sub-sec:impr-dbms} \\
    \texttt{U2} & Improve or extend the \gls{cmb} system's usability features. & \Cref{sec:real-time}, \ref{sub-sec:impr-views-feedback}, and \ref{subsec:impr-database} \\
    \texttt{U3} & Conduct a user-experiment to evaluate system usability. & \Cref{sec:cont-user-testing} and \ref{sec:user-testing} \\ \hline
    \texttt{P1} & Propose improvements to the existing stability test. & \Cref{sub-sec:prop-stability-test} \\
    \texttt{P2} & Propose improvements to the HowTo-page and existing problem descriptions, and add new problems. & \Cref{sub-sec:prop-howto} and \ref{sub-sec:prop-problems} \\
    \texttt{P3} & Propose how to implement a discussion forum. & \Cref{sub-sec:prop-forum} \\
    \end{tabular}
    \caption{Thesis contributions}
    \label{tab:contributions}
\end{table}
\renewcommand{\arraystretch}{0.0}
\endgroup

\section{Outline}
\label{sec:out}
This report is structured as follows:\\

\textbf{Chapter \ref{ch:background}}: The chapter presents the Mont Blanc project, which motivated the Climbing Mont Blanc project. The chapter will also present the Climbing Mont Blanc project, that is, the system architecture, energy measurement method, the system environment, and system security. The chapter will also present the theme of another Master Thesis working to improve system scalability. Finally, related \glspl{oj} and other related work concludes the chapter. \\

\textbf{Chapter \ref{ch:design}}: The chapter presents the definition of usability in software systems. Based on theory, aspects which makes an \gls{oj} usable are briefly discussed. The chapter ends with a discussion of the objectives set by this thesis and their relevance to the usability definition. \\

\textbf{Chapter \ref{ch:improvements}}: The chapter presents implementation done to the system in this work. The chapter will present the technical solutions for the usability goals set in \Cref{sec:ps-inter}, as well as present implementation proposals for a improved stability test, improved HowTo-information and base of provided problems, and a discussion forum. \\

\textbf{Chapter \ref{ch:testing}}: The chapter starts with a presentation of continuous user testing conducted during development. The chapter will also present a user experiment and analyze wether the usability has improved after implementing the usability features mentioned in \Cref{sec:ps-inter}. The chapter ends with a presentation of system unit test coverage, to justify the correctness of implemented features. \\

\textbf{Chapter \ref{ch:evaluation}}: An evaluation and discussion of the technologies used and user test pros and cons will be discussed in this chapter. The chapter also presents alternatives to technologies and the user test methodology. The chapter ends with a discussion on wether the objectives presented in \Cref{sec:ps-inter} have been reached. \\

\textbf{Chapter \ref{ch:conclusion}}: The chapter concludes the thesis, and presents future work suggestions based on results of the user experiment and suggested improvements listed in Appendix \ref{apdx:backlog}.



%There are also many appendices attached to this thesis due to a request from the main supervisor.
